Meta-analysis for the Effect of SSRIs on Anxiety

### 2023-06-13 manuscript/manuscript.Rmd
fix HED, add dose to forest plots

#Write forest plot to file
xname <- paste0("Hedges' g (", p, ")")
tmp <- df[order(df$vi, decreasing = TRUE), ]
tmp$paperlabel <- paste(tmp$paper, tmp$type.of.ssri.and.dose)
df_es <- data.frame(
    Study = ordered(tmp$paperlabel, levels = unique(tmp$paperlabel)),
    y = 1:nrow(tmp),
    es = tmp$yi,
    lb = tmp$yi - 1.96*sqrt(tmp$vi),
    ub = tmp$yi + 1.96*sqrt(tmp$vi),
    Sample = p)

>>>>

#Write forest plot to file
xname <- paste0("Hedges' g (", p, ")")
tmp <- df[order(df$vi, decreasing = TRUE), ]
tmp$paperlabel <- paste(tmp$paper, tmp$type_ssri_and_dose)
df_es <- data.frame(
    Study = ordered(tmp$paperlabel, levels = unique(tmp$paperlabel)),
    y = 1:nrow(tmp),
    es = tmp$yi,
    lb = tmp$yi - 1.96*sqrt(tmp$vi),
    ub = tmp$yi + 1.96*sqrt(tmp$vi),
    Sample = p)
